\documentclass[margin,line]{resume}
\usepackage{graphicx}
%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Quyuan Luo}
    %__________________________________________________________________________________________________________________
    % Contact Information
    \begin{resume}
    \section{\mysidestyle Affiliation}
    State Key Lab. of Integrated Service Networks (\textsl{ISN})  \\
    Mail Box 88, Xidian University       \\
    No.2 South Taibai Road             \hfill \textsl{Mobile: (+86)18302999110}     \\
    Xi'an, Shaanxi, 710071, China      \hfill \textsl{E-mail: qyluoxidian@163.com}
    \vspace{-0mm}
    %__________________________________________________________________________________________________________________
            % personal information
    \section{\mysidestyle Personal\\Information}
    \textsl{Gender:} Male \\
    \textsl{Date of Birth:} 03/29/1993 \\
    \textsl{Nationality:} China
    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
     Xidian University, Xi'an, China
    \begin{list2}
    \item  Ph.D. in Communications and Information Systems, Sep. 2016$-$present
    \item  M.Eng. in Communications and Information Systems, Sep. 2015$-$Jun. 2016
    \end{list2}\vspace{-3mm}
    Changchun University of Science and Technology (CUST), changchun, China
    \begin{list2}
    \item  B.S. in Telecommunications Engineering, Sep. 2011$-$Jun. 2015 \\
        \textbf{Rank No. 7 in four-year average GPA }
    \end{list2}
    \vspace{-0mm}
%__________________________________________________________________________________________________________________
            % Honors and Awards
    \section{\mysidestyle Honors \\ and Awards}
    {\begin{list2}
    \item 2018: First Class Scholarship and Excellent Postgraduate Student Award in Xidian University
    \item 2017: First Class Scholarship and Excellent Postgraduate Student Award in Xidian University
    \item 2016: Second Class Scholarship in Xidian University
    \item 2015: Second Class Scholarship in CUST
    \item 2014: First Class Scholarship in CUST
    \item 2013: National Encouragement Scholarship, Second Prize in Contemporary Undergraduate Mathematical Contest in Modeling, First Prize in Mathematical Competition of CUST, First and Second Class Scholarship in CUST
    \item 2012 National Encouragement Scholarship, First and Second Class Scholarship in CUST
    \end{list2}}
    \vspace{-0mm}
    %__________________________________________________________________________________________________________________
        % course
    \section{\mysidestyle Main Courses\\Taken}
    \begin{list2}
        \item Mathematics: Probability Theory, Stochastic Process, Convex Optimization, Numerical Functional, Wavelet Analysis.
        \item Computer:  Matlab, C, Computer Networks
        \item Communications: Signals and Systems, Principle of Communications, Digital Communications, Wireless Communications, Digital Signal Processing.
    \end{list2}
    \vspace{-0mm}
%__________________________________________________________________________________________________________________
      % Language
      \section{\mysidestyle Language}
      CET-6: China College English Test Band-6, 2013 \\
      PETS-5: Public English Test System-5, 2018
      \vspace{-0mm}
    %__________________________________________________________________________________________________________________
      % Research Interests
    \section{\mysidestyle Research\\Interests}

    \textbf{Intelligent Transportation Systems}
    \vspace{0.5mm}
    \\
    %\vspace{1mm}%
    Content distribution and resource allocation in vehicular networks, joint allocation of communication and computing resources for networked autonomous driving, vehicle-road collaborative networked intelligent driving.
    \vspace{-0mm}
    %___________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Publications}
%    \Centering
%    \Subsection{\Mysidestyle Published}
   \begin{list2}
    \item Changle Li, \textbf{Quyuan Luo}, Guoqiang Mao, Min Sheng and Jiandong Li, ``Vehicle-Mounted Base Station for Connected and Autonomous Vehicles: Opportunities and Challenges," \emph{IEEE Wireless Communications} (\textbf{minor revise}), 2018.

  \item \textbf{Quyuan Luo}, Changle Li, Tom H. Luan and Yingyou Wen, ``Optimal Utility of Vehicles in LTE-V Scenario: An Immune Clone Based Spectrum Allocation Approach," \emph{IEEE Transactions on Intelligent Transportation Systems}, PP. 1-12, 2018, early access.

  \item   \textbf{Quyuan Luo}, Xuelian Cai, Tom H. Luan and Qiang Ye, ``Fuzzy Logic-Based Integrity-Oriented File Transfer for Highway Vehicular Communications," EURASIP Journal on Wireless Communications and Networking, 2018, 2018(1):3.

  \item \textbf{Quyuan Luo}, Changle Li, Qiang Ye, Tom H. Luan, Lina Zhu and Xiaolei Han, ``CFT: A Cluster-based File Transfer Scheme for Highway VANETs," in \emph{Proc. IEEE ICC}, Paris, 2017, pp. 1-6.

  \item Changle Li, \textbf{Quyuan Luo}, Guoqiang Mao, Min Sheng and Jiandong Li, ``Vehicle-Mounted Base-Station based Communication Network Architecture for Connected Autonomous Vehicles," accepted to appear in \emph{Journal of Beijing Jiaotong University}. (in Chinese)

  \item Pengfei Huang, Changle Li, \textbf{Quyuan Luo}, Yao Zhang and Bing Xia, ``GECM: A Novel Green Wave Band Based Energy Consumption Model for Electric Vehicles," in \emph{Proc. IEEE VTC-Spring}, Porto, 2018, pp. 1-5.

  \item Zhifang Miao, Xuelian Cai, \textbf{Quyuan Luo}, Weiwei Dong, ``A FLRBF Scheme for Optimization of Forwarding Broadcast Packets in Vehicular Ad Hoc Networks," in \emph{Proc. IEEE PIMRC}, Valencia, 2016, pp. 1-5.

  \end{list2}
%______________________________________________________________________________________________________________________
\end{resume}
\end{document}

